Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-10-10 summary.tex
10.10

We develop a boolean operation method based on vertex-based representation of mesh (e.g., halfedge) and embed plane-based techniques into it, requiring only one-time conversion to the plane representation in intersection areas. It allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods. In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations. Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation. The major difficulty of embed P-rep on vertex-based representation is by the incoherence between the two representations. Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on vertex-based representations can be very complex and thus inefficient under P-rep. On the other hand, we have to compute all under P-rep for exactness and robustness. Therefore, we manage to limit our computation of boolean operations to several basic plane-based geometry predicates. The experiment shows that our method is much faster than exact, robust methods, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.

@@

Boolean operations have long been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Most previous work of boolean operations can be classified into two categories: exact and approximate methods. Exact methods retain vertex positions. And the topology of the input meshes is also preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection. However, the coordinates cannot be represented exactly using fix-precision float point numbers and the robustness is often a problem. Using exact arithmetic is too expensive in computing. Therefore, exact methods face the problem of the balance between performance and robustness. On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images and can reach better performance and robustness.

@@

For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases such as coplanar conditions. Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is often inevitable. Douze et al. \cite{douze2015quickcsg} implemented very efficient boolean operations that can handle very large meshes. Also, their method is able to perform variadic boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of binary boolean operations. However, their method cannot deal with coplanar cases nor guarantee accuracy for common situations. On the contrary, CSGs with large meshes contain are more complex and more likely to contain degenerate cases. Also, coplanar cases can regularly happens for man-made artifact modeling (Fig. \ref{fig:coplanarexample}) and should not be treated as exceptions for boolean operation methods.

>>>>

We develop a boolean operation method based on B-reps of meshes with geometry connectivity (e.g., halfedge). We further embed P-rep of faces into the B-rep, forming a hybrid representation, which allows us to take the advantage of both representations. This hybrid representation is fast that requires only one-time conversion to the P-rep in intersection areas of meshes.
%that allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods.
In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations. Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation. The major difficulty of embed P-rep into B-rep is caused by the incoherence between the two representations. Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on B-reps can be very complex and thus inefficient under P-rep. On the contrary, all computations have to be performed under P-rep for exactness and robustness. Therefore, we manage to constrain our computation to several basic plane-based geometry predicates. The experiment shows that our method is much faster than exact, robust methods, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.

@@

Boolean operations have been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Previous work of boolean operations can be classified into two categories: exact and approximate methods. Exact methods retain vertex positions. And the topology of the input meshes is also preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection. However, the coordinates cannot be represented exactly using fix-precision float-point numbers and the robustness is often a problem. However, using exact arithmetic is too expensive in computing. Therefore, exact methods face the problem of the balance between performance and robustness. On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images and can reach better performance and robustness.

@@

For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases such as coplanar conditions. Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is inevitable. Douze et al. \cite{douze2015quickcsg} implemented very efficient boolean operations that can handle very large meshes. Also, their method is able to perform non-incremental boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of incremental boolean operations. However, their method can neither deal with coplanar cases nor guarantee accuracy for common situations. On the contrary, CSGs with large number of faces contain are more complex and more likely to contain degenerate cases. Also, coplanar cases can regularly happens for man-made artifact modeling (Fig. \ref{fig:coplanarexample}) and should not be treated as exceptions for boolean operation methods.
